Preferences interact: what consequences for a Schelling scenario?

### 2019-12-02 ethnic_value_rum.Rmd
Add files via upload

>>>>

```{r att_income , include=TRUE}

f_att <- function(i,b){   # utility function as single-peaked
 A <- 1 / (1 + exp(-b(i)))
}

  b <- 0.5

a_0 <- f_cst(a,0)
a_1 <- f_cst(a,0.1)
a_2 <- f_cst(a,0.2)
a_3 <- f_cst(a,0.3)
a_4 <- f_cst(a,0.4)
a_5 <- f_cst(a,0.5)
a_6 <- f_cst(a,0.6)
a_7 <- f_cst(a,0.7)
a_8 <- f_cst(a,0.8)
a_9 <- f_cst(a,0.9)
a_10 <- f_cst(a,1)

Prob_A <- c(a_0,a_1,a_2,a_3,a_4,a_5,a_6,a_7,a_8,a_9,a_10)
income <- seq(0,i, by = 0.1)

plot(price,na.omit(utility),ylab = "utility_ec",xlab="price", main = paste0("income =",i))

```{r income_price , include=TRUE}

# tentative of utility economic, given by the difference (income - price), so to represent how convenient a location is. 
# ideally identity equation: if income < price, probability would be 0. If beta is negative, the probability could still be computed, which is nonsense

f_cst <- function(i,p){   # utility function as single-peaked
 if (i < p){
    U <- NA}else{
  U <- ((i - p) / i)}
}

  i <- 0.5

i_0 <- f_cst(i,0)
i_1 <- f_cst(i,0.1)
i_2 <- f_cst(i,0.2)
i_3 <- f_cst(i,0.3)
i_4 <- f_cst(i,0.4)
i_5 <- f_cst(i,0.5)
i_6 <- f_cst(i,0.6)
i_7 <- f_cst(i,0.7)
i_8 <- f_cst(i,0.8)
i_9 <- f_cst(i,0.9)
i_10 <- f_cst(i,1)

utility <- c(i_0,i_1,i_2,i_3,i_4,i_5,i_6,i_7,i_8,i_9,i_10)
price <- seq(0,i, by = 0.1)

plot(price,na.omit(utility),ylab = "utility_ec",xlab="price", main = paste0("income =",i))
